\plaintitle

### 2016-05-26 paper/paper.tex
Change in figures
Small reference update

\usepackage[backend=biber, style=draft]{biblatex}
%\usepackage{custom}

@@

The entire history of the NBA and the best teams were analyzed by
fivethirtyeight~\cite{fivethirtyeight}. They calculated an ELO-score\cite{eloraring} 
for all teams an visualized them on line graphs.

@@

\begin{figure}
\centering
  \includegraphics[width=1.0\columnwidth]{figures/presidentcandidatesvisualization}
  \caption{The path of president candidates in their road to become president.}~\label{fig:whitehousepath}
\end{figure}

@@

\begin{figure}
\centering
  \missingfigure{}
%  \includegraphics[width=0.9\columnwidth]{figures/playoffviewfirstimplemantation}
  \caption{First implementation of the play-off view.}~\label{fig:firstimplementationplayoffview}
\end{figure}

@@

\printbibliography
\todo{References should be in alphabetical order and represented by numbers in the text. Style should be set to style{SIGCHI-Reference-Format}, this moment it is set to the style draft}

>>>>

\usepackage[backend=biber, style=numeric, firstinits=true, url=false, sorting=none]{biblatex}
%\usepackage{custom}

@@

The entire history of the NBA and the best teams were analyzed by
fivethirtyeight~\cite{fivethirtyeight}. They calculated an ELO-score\cite{elorating} 
for all teams an visualized them on line graphs.

@@

%\begin{figure}
%\centering
%  \includegraphics[width=1.0\columnwidth]{figures/presidentcandidatesvisualization}
%  \caption{The path of president candidates in their road to become president.}~%\label{fig:whitehousepath}
%\end{figure}

@@

\begin{figure}
\centering
%  \missingfigure{}
  \includegraphics[width=0.9\columnwidth]{figures/playoffviewfirstimplemantation}
  \caption{First implementation of the play-off view.}~\label{fig:firstimplementationplayoffview}
\end{figure}

@@

\printbibliography

\todo{References should be in alphabetical order and represented by numbers in the text. Style should be set to style{SIGCHI-Reference-Format}, this moment it is set to the style draft}
